---
title: "Group 7 - R Assignment [Resubmission]"
output: pdf_document
---

```{r}
vgsales <- read.csv("vgsales.csv")
```

**Task 1 - Print the structure of your dataset**

**author: Yi Ban**

```{r}
print(str(vgsales))
```

**Task 2 - List the variables in your dataset**

**author: Yi Ban**

```{r}
names(vgsales)
```

**Task 3 - Print the top 15 rows of your dataset**

**author: Yi Ban**

```{r}
print(head(vgsales,n=15))
```

**Task 4 - Write a user defined function using any of the variables from the data set.**

**author: Sriram Govindapuram Ramani**

```{r}
userdefinedfunction = function(x,y){x/2+4 + y/5+2}
userdefinedfunction(vgsales$NA_Sales,vgsales$PAL_Sales)
```

**Task 5 - Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset.**

**author: Sriram Govindapuram Ramani**

```{r}
filter(vgsales,vgsales$Publisher=="Nintendo")
```

**Task 6 - Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset.**

**author: Geetanjali Arora**

```{r}
newvgsales = cbind(vgsales$User_Score, vgsales$Critic_Score, vgsales$Total_Shipped)
View(newvgsales)
newvgsales = as.data.frame(newvgsales)
names(newvgsales)[1]="User_Score"
names(newvgsales)[2]="Critic_Score"
names(newvgsales)[3]="Total_Shipped"
```

**Task 7 - Remove missing values in your dataset**

**author: Geetanjali Arora**

```{r}
vgsales_na_omit <- na.omit(vgsales)
```

**Task 8 - Identify and remove duplicated data in your dataset**

**author: Geetanjali Arora**

```{r}
duplicated(vgsales)
which(duplicated(vgsales))
vgsales_no_duplicates <- vgsales[!duplicated(vgsales),]
```

**Task 9 - Reorder multiple rows in descending order**

**author: Ethan Zatzman**

```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
```

```{r}
vgsales = vgsales %>% arrange(desc(User_Score))
vgsales %>% select(User_Score)
```

**Task 10 - Rename some of the column names in your dataset**

**author: Ethan Zatzman**

```{r}
names(vgsales)[names(vgsales)=="ESRB_Rating"]<- "Rating"
```

```{r}
names(vgsales)[names(vgsales)=="Platform"]<- "Console"
```

```{r}
vgsales %>% select(Rating,Console)
```

**Task 11 - Add new variables in your data frame by using a mathematical function (for e.g. -- multiply an existing column by 2 and add it as a new variable to your data frame)**

**author: Poy Potenciano**

```{r}
dplyr::mutate(vgsales, Rank = 2*Rank)
```

**Task 12 - Create a training set using random number generator engine.**

**author: Poy Potenciano**

```{r}
RandomNum <- runif(50, 1, 99)
RandomNum
```

**Task 13 - Print the summary statistics of your dataset**

**author: Sriram Govindapuram Ramani**

```{r}
summary(vgsales)
```

**Task 14 - Use any of the numerical variables from the dataset and perform the following statistical functions • Mean • Median • Mode • Range**

**author: Ethan Zatzman**

*Mean*

```{r}
mean_of_user_score <- mean(na.omit(vgsales$User_Score))
mean_of_user_score #
```

*Median*

```{r}
mean_of_user_score <- mean(na.omit(vgsales$User_Score))
mean_of_user_score #
```

*Mode*

```{r}
freq_of_user_score <- data.frame(table(vgsales$User_Score))
mode_of_user_score <- max(freq_of_user_score$Freq)
freq_of_user_score #
mode_of_user_score #
```

*Range*

```{r}
range_of_user_score <- range(na.omit(vgsales$User_Score))
range_of_user_score #
```

**Task 15 - Plot a scatter plot for any 2 variables in your dataset**

**author: Muhammed Aqib Arif Ahamed**

```{r}
plot(vgsales$Critic_Score, vgsales$Total_Shipped, xlab = 'Critic Score', ylab = 'Total Games Shipped')
```

**Task 16 - Plot a bar plot for any 2 variables in your dataset**

**author: Muhammed Aqib Arif Ahamed**

```{r}
ggplot(data = vgsales) + geom_bar(aes(x = Critic_Score, fill=as.factor(Total_Shipped)))
```

**Task 17 Find the correlation between any 2 variables by applying least square linear regression model author: Poy Potenciano**

```{r}
X <- vgsales[,"Critic_Score"]
Y <- vgsales[,"User_Score"]
```

```{r}
head(X)
head(Y)

xycorr <- cor(Y,X, method = "pearson")
xycorr #
```

# **GITHUB FILE**

## Click the link below:

## [**Group 7 - R Assignment Github Repository**](https://github.com/poypotenciano/Group-7-Assignment-2-Data-Analysis-using-R-Programming.git)
